---
title: "Development actions history"
output: html_document
editor_options: 
  chunk_output_type: console
---

All commands that you use to use when developing packages...

# First time just after creating the project

-   Fill the following chunk to create the DESCRIPTION of your package

```{r description, eval=FALSE}
# Describe your package
fusen::fill_description(
  pkg = here::here(),
  fields = list(
    Title = "YABPstat: Yet Another BPstat",
    Description = "A package that allows using the BPStat - Estatísticas Online, from Banco de Portugal, public API to access statistical activity for reference purposes (more information in: https://bpstat.bportugal.pt/avisos-legais).",
    `Authors@R` = c(
      person(given  = "Henrique", family  = "Luís", email = "halsa@iscte-iul.pt", role = c("aut"), comment = c()),
      person(given  = "Maria", family  = "Ribeiro", email = "mcroo2@iscte-iul.pt", role = c("aut"),comment = c()),
      person(given  = "Nelson", family  = "Jesus", email = "nelson_carvalho_jesus@iscte-iul.pt", role = c("aut", "cre"),comment = c()),
      person(given  = "Pedro", family  = "Ferreira", email = "pvfaa@iscte-iul.pt", role = c("aut"),comment = c()),
      person(given  = "Telma", family  = "Garção", email = "telma_garcao2@iscte-iul.pt", role = c("aut"),comment = c())
    )),
  overwrite = TRUE
)
# Define License with use_*_license()
usethis::use_mit_license(copyright_holder = c("Nelson Jesus, Telma Garção"))
```

# Start using git

```{r, eval=FALSE}
usethis::use_git()
# Deal with classical files to ignore
usethis::git_vaccinate()
# Use main for primary branch
usethis::git_default_branch_rename()

usethis::use_build_ignore(".git")
```

# Set extra sources of documentation

```{r, eval=FALSE}
# Install a first time
remotes::install_local()
# README
usethis::use_readme_rmd()
# Code of Conduct
usethis::use_code_of_conduct("contact@fake.com")
# NEWS
usethis::use_news_md()
```

**From now, you will need to "inflate" your package at least once to be
able to use the following commands. Let's go to your flat template, and
come back here later if/when needed.**

# Package development tools

## Use once

```{r, eval=FALSE}
# Pipe
usethis::use_pipe()

# package-level documentation
usethis::use_package_doc()

# GitHub
# Add your credentials for GitHub
usethis::create_github_token()
gitcreds::gitcreds_set()

# _All-in-one share of your package and its documentation on GitHub
fusen::init_share_on_github()

# _Or one step at a time
# Send your project to a new GitHub project (included in `init_share_on_github()`)
usethis::use_github()

# Set Continuous Integration
# _GitHub (included in `init_share_on_github()`)
usethis::use_github_action_check_standard()
usethis::use_github_action("pkgdown")
usethis::use_github_action("test-coverage")
# _GitLab
gitlabr::use_gitlab_ci(type = "check-coverage-pkgdown")
```

## Use everytime needed

```{r}
# Simulate package installation
pkgload::load_all()

# desinstalação do package
devtools::unload("yabpstat")

# Generate documentation and deal with dependencies
attachment::att_amend_desc()

# Check the package
devtools::check()

# Add a new flat template
fusen::add_flat_template("add")
```

# Share the package

```{r}
# set and try pkgdown documentation website locally
usethis::use_pkgdown()

pkgdown::build_site()

# build the tar.gz with vignettes to share with others
devtools::build(vignettes = TRUE)

# Share your package and its documentation on GitHub
# usethis::create_github_token()
# gitcreds::gitcreds_set()
fusen::init_share_on_github()
```

```{r}
fusen::inflate(flat_file = "dev/flat_full.Rmd", vignette_name = "Get started", overwrite = TRUE)
```


