---
title: "flat_full.Rmd for working package"
output: html_document
editor_options: 
  chunk_output_type: console
---


```{r include=FALSE}
library(testthat)
library(httr2)
library(jsonlite)
library(DT)
library(tidyr)
library(dplyr)
library(dygraphs)
library(xts)
library(utils)
library(htmltools)

```

<!--
 You need to run the 'description' chunk in the '0-dev_history.Rmd' file before continuing your code there.

If it is the first time you use {fusen}, after 'description', you can directly run the last chunk of the present file with inflate() inside.
--> 

```{r load, include=FALSE}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)


```

```{r dataset, include=FALSE}
# Run all this chunk in the console directly
pkgload::load_all(path = here::here(), export_all = FALSE)

```

```{r function-ya_status_codes}
#' ya_status_codes
#'
#' data in top_level.
#'
#' @format ## "ya_status_codes"
#' A data frame with 63 rows and 3 variables representing the available status codes in Portuguese and English languages:
#' \describe{
#'   \item{ status_code }{  character }
#'   \item{ description_en }{  character }
#'   \item{ description_pt }{  character }
#' }
#' @source https://developer.mozilla.org/en-US/docs/Web/HTTP/Status & https://developer.mozilla.org/pt-BR/docs/Web/HTTP/Status.
#' 
#' data(ya_status_codes)
#' "ya_status_codes"

```


```{r function-ya_favourites}
#' ya_favourites
#'
#' data in top_level.
#'
#' @format ## "ya_favourites"
#' A data frame with 15 rows and 1 variable, choosen from BPstat observations carousel, representing the user's favourite series ID from BPstat:
#' \describe{
#'   \item{ series_id }{  numeric }
#' }
#' @source YABPstat
#' 
#' data(ya_favourites)
#' "ya_favourites"

```



```{r function-check_language}
#' Title: check_language()
#' 
#' Description: An helper function that serves as a validation check for user input of the BPstat API supported languages. Currently it uses Portuguese (PT) and English (EN) languages
#' 
#' @param lang A string that represents the languages supported by BPstat API. Currently only uses "PT" or "EN". Defaults to "EN"
#' 
#' @return Returns an error message if user inputs other option than "PT", "pt", "EN" or "en". It doesn't return any message if the task has been successfully accomplished
#' 
#' @noRd
#' 
check_language <- function(lang) {
  if (!(lang %in% c("EN", "en", "PT", "pt"))) {
    err_msg_lang <- paste0(
      "At the moment there is no support for that language.",
      "\n",
      "Please choose between \"PT\" ou \"EN\"."
    )
    stop(err_msg_lang)
  }
  
}

```
  

  
```{r tests-check_language, eval = FALSE}
#' \dontrun{
#'test_that("check_language works", {
#'  expect_null(check_language(lang = "PT"))
#'  expect_error(check_language(lang = "FR"))
#'})
#'}
```




```{r function-check_status_code}
#' Title: check_status_code()
#' 
#' Description: An helper function that checks the response call to BPstat API, used in many different functions in the YABPstat package.
#' 
#' @param st_code Status code returned by a call to BPstat API
#' @param lang A string that represents the languages supported by BPstat API. Currently only uses "PT" or "EN". Defaults to "EN"
#' 
#' @importFrom dplyr filter
#' @importFrom dplyr select
#' @importFrom dplyr %>%
#' 
#' @return Returns a string with the description in Portuguese or English languages, of the status code returned from BPstat API call.
#' 
#' @noRd
#' 
check_status_code <- function(st_code, lang = "EN") {

  check_language(lang)
  
  fich <- system.file("ya_status_codes.rds",package = "yabpstat", mustWork = TRUE)
  
  stat_codes <- readRDS(file = fich)
  
  stat_codes <- stat_codes %>%
      dplyr::filter(status_code == st_code)
  
  if (length(stat_codes) == 0){
    
    stop("That status doesn't exists yet.")
    
  } else if (lang == "EN" | lang == "en") {
    
    stat_codes <- stat_codes %>%
      dplyr::select(description_en)
    
    return(stat_codes)
    
  } else if (lang == "PT" | lang == "pt") {
    
    stat_codes <- stat_codes %>%
      dplyr::select(description_pt)
    
    return(stat_codes)
    
  }
}

```

  
```{r tests-check_status_code}

#' Test with your dataset in "data/"
#' 
#'\dontrun{
# datafile <- "data/ya_status_codes.rds"
# 
# if(!file.exists(datafile)){
#   
#   datafile <- file.path("tests", "testthat", datafile)
#   if (!file.exists(datafile)) {stop(datafile, " does not exist.")}
#   
# }
# 
# stat_codes <- readRDS(file = datafile)
# 
# test_that("check_status_code works", {
#   expect_type(check_status_code(200), "list")
#   # expect_error(check_status_code(900), "That status doesn't exists yet.")
# })
# }
```
  

```{r function-check_api_version}

#' Title: check_api_version()
#' 
#' Description: An helper function that checks for the BPstat Data API version present in "https://bpstat.bportugal.pt/data/docs?format=openapi"
#' 
#' @param bpstat_api_version A string that represents version of current BPStat API
#' 
#' @return Returns an message with the current API version
#' 
#' @noRd
#' 
check_api_version <- function(bpstat_api_version) {
  if (bpstat_api_version[[2]][[3]] == "v1") {
    return("v1")
    
  } else {
    return(bpstat_api_version[[2]][[3]])
  }
}
```
  

  
```{r tests-check_api_version, eval = FALSE}
#' \dontrun{
#'test_that("check_api_version works", {
#'  expect_true() 
#'})
#' }
```
  


    
```{r function-check_extension}
#' Title: check_extension
#' 
#' Description: This is an helper function that checks if the save output function complies with the requirements of saving files with rds or csv extensions
#' 
#' @param extension A string that represents an extension to save information in BPstat to an external file. At the moment there is support only to rds and csv extensions.
#' 
#' @return An error message if it is any other format besides rds or csv. Nothing if it all goes well.
#' 
#' @noRd
#' 
check_extension <- function(extension) {
  if (!(extension %in% c("RDS", "rds", "csv", "CSV"))) {
    err_msg_extension <- paste0(
      "The extension is not supported, yet.",
      "\n",
      "Please choose between \"rds\" or \"csv\"."
    )
    stop(err_msg_extension)
  }
  
}

```
  

  
```{r tests-check_extension}
#' \dontrun{
#' test_that("check_extension works", {
#'   expect_null(check_extension(extension = "rds"))
#'   expect_error(check_extension(extension = "txt")) 
#' })
#' }
```



```{r function-generate_datasets}
#' Title: generate_datasets()
#' 
#' Description: This is an helper function that given an href from a BPstat dataset, it returns a dataframe with the follow information: version, href, class, source
#' 
#' @importFrom httr2 request
#' @importFrom httr2 req_user_agent
#' @importFrom httr2 req_perform
#' @importFrom jsonlite fromJSON
#' @importFrom jsonlite flatten
#' @importFrom dplyr mutate
#' @importFrom dplyr %>%
#' 
#' @return A dataframe with information about datasets, namely: version, href, class, source
#' 
#' @noRd
#' 
generate_datasets <- function(dataset_href){

  max_datasets <- 100
  
  url <- paste0(dataset_href, "&page_size=", max_datasets)
  
  response <- httr2::request(url) %>%
    httr2::req_user_agent("YABPstat package") %>% 
    httr2::req_perform()
  
  content_df <- response %>% 
    httr2::resp_body_raw() %>% 
    rawToChar() %>% 
    jsonlite::fromJSON()

  datasets_df <- jsonlite::flatten(content_df$link$item)
  
  datasets_df <- datasets_df %>% 
    dplyr::mutate(version = content_df$version,
                  href = content_df$href,
                  class = content_df$class,
                  source = content_df$source)
  
  return(datasets_df)
  
}
```

  
```{r tests-generate_datasets}
#' \dontrun{
#'test_that("generate_datasets works", {
#'  expect_true(inherits(generate_datasets, "function")) 
#'})
#'}
```

    
```{r function-generate_dimensions}

#' Title: generate_dimensions()
#' 
#' Description: This is an helper function that given an href from a BPstat dimension, it returns a dataframe with the follow information: version, href, class, source, item label, item class, item href 
#' 
#' @param dimensions_href An href that represents the path to a dimension in BPstat
#' 
#' @importFrom httr2 request
#' @importFrom httr2 req_user_agent
#' @importFrom httr2 req_perform
#' @importFrom jsonlite fromJSON
#' @importFrom jsonlite flatten
#' @importFrom dplyr mutate
#' @importFrom dplyr %>%
#' 
#' @return A dataframe with information about dimensions, namely: version, href, class, source, item label, item class and item href
#' 
#' @noRd
#' 
generate_dimensions <- function(dimensions_href){
  
  max_datasets <- 100
  
  url <- paste0(dimensions_href, "&page_size=", max_datasets)
  
  response <- httr2::request(url) %>% 
    httr2::req_user_agent("YABPstat package") %>% 
    httr2::req_perform()

  bpstat_dimensions <- jsonlite::fromJSON(rawToChar(response$body))
  
  bpstat_dimensions_item <-
    jsonlite::flatten(bpstat_dimensions$link$item$extension)
  
  bpstat_dimensions_item <- bpstat_dimensions_item %>%
    dplyr::mutate(version = bpstat_dimensions$version,
                  dimensions_href = bpstat_dimensions$href,
                  class = bpstat_dimensions$class,
                  source = bpstat_dimensions$source,
                  item_label = bpstat_dimensions$link$item$label,
                  item_class = bpstat_dimensions$link$item$class,
                  item_href = bpstat_dimensions$link$item$href)
  
  return(bpstat_dimensions_item)
    
}

```

  
```{r tests-generate_dimensions}
#' \dontrun{
#' test_that("generate_dimensions works", {
#'   expect_true(inherits(generate_dimensions, "function")) 
#' })
#' }
```


    
```{r function-save_output}
#'
#' Title: save_output
#' 
#' Description: An helper function that allows easyly saving data from YABPstat functions to user's local folder for further use. By default it creates a "data/raw/" folder. 
#' 
#' @param r_object The name of the R object to save
#' @param file_directory The default folder name where the file is saved. Defaults to: "data/raw/"
#' @param file_name The name of the file to be saved
#' @param extension The extension name which the file is saved. It only supports "rds" and "csv" for the moment. Defaults to "rds".
#' 
#' @return A file with extension "rds" or "csv"
#' 
#' @noRd

save_output <- function(r_object, file_directory = "raw", file_name, extension = "rds"){
  
  check_extension(extension)
  
  if (!dir.exists(paste0(getwd(),
                         "/data/",
                         file_directory))) {
    dir.create(file.path("data", file_directory), recursive = TRUE)
  }
  
  if (extension == "rds" || extension == "RDS") {
    saveRDS(
      object = r_object,
      file = paste0(getwd(),
                    "/data/",
                    file_directory,
                    "/",
                    file_name,
                    ".rds")
    )
  } else if (extension == "csv" || extension == "CSV") {
    write.csv(
      r_object,
      file = paste0(getwd(),
                    "/data/",
                    file_directory,
                    "/",
                    file_name,
                    ".csv"),
      row.names = TRUE
    )
    
  }
  
}
```
  

  
```{r tests-save_output}
#'\dontrun{}
# test_that("save_output works", {
#   expect_true(inherits(save_output, "function")) 
# })
#}
```
  

    
```{r function-plot_serie}
#'
#' Title: plot_serie()
#' 
#' Description: This is an helper function to plot series from the main function ya_info_serie()
#' 
#' @param id A serie ID from the BPstat.
#' @param lng A string that represents the languages supported by BPstat API. Currently only uses "PT" or "EN". Defaults to "EN"
#' 
#' @importFrom httr2 request
#' @importFrom httr2 req_user_agent
#' @importFrom httr2 req_perform
#' @importFrom httr2 resp_status
#' @importFrom dplyr between
#' @importFrom dplyr %>%
#' @importFrom dplyr tibble
#' @importFrom tidyr unnest_longer
#' @importFrom tidyr unnest_wider
#' @importFrom dplyr mutate
#' @importFrom dplyr across
#' @importFrom dplyr select
#' @importFrom dplyr rename
#' @importFrom jsonlite fromJSON
#' @importFrom jsonlite read_json
#' @importFrom xts xts
#' @importFrom dygraphs dygraph
#' @importFrom dygraphs dyOptions
#' @importFrom dygraphs dyRangeSelector
#' @importFrom dygraphs dyCrosshair
#' @importFrom dygraphs dyAxis
#' @importFrom dygraphs dyAxis
#' 
#'  
#' 
#' @return A plot with the data gather from BPstat from the designated serie, chosen by the user
#' 
#' @noRd
#' 
plot_serie <- function(id, lng){

  basepath <- "https://bpstat.bportugal.pt"
  
  url_sv <- paste0(basepath,
                   "/api/observations/?series_ids=",
                   id)
  
  url_sfv <- paste0(basepath,
                    "/api/series/?view_full=true&page_size=1&series_ids=",
                    id)

  response <- httr2::request(url_sfv) %>%
    httr2::req_user_agent("YABPstat package") %>%
    httr2::req_perform()

  st_c <- httr2::resp_status(response)
  
  status_description <-
    check_status_code(st_c, lng)
  
  if (dplyr::between(st_c, 300, 550)) {
    stp_msg <- paste0("Estado :",
                      st_c,
                      " - ",
                      status_description,
                      ".")
    
    stop(stp_msg)
  }

  url_sv_json <- jsonlite::read_json(url_sv)
  
  df_plot <- url_sv_json %>%
    dplyr::tibble() %>%
    tidyr::unnest_longer(1) %>%
    tidyr::unnest_wider(1) %>%
    dplyr::mutate(dplyr::across(reference_date, as.Date)) %>%
    dplyr::select(reference_date, value) %>%
    dplyr::rename(ds = reference_date, y = value)
  
  url_sfv_json <- jsonlite::fromJSON(url_sfv)
  
  if (lng == "EN" || lng == "en") {
    titulo <- url_sfv_json[["data"]][["title"]][["EN"]]
    
    
  } else {
    titulo <- url_sfv_json[["data"]][["title"]][["PT"]]
    
  }

  dados <- xts::xts(x = df_plot$y, order.by = df_plot$ds)
  
  
  dygraphs::dygraph(dados, main = titulo) %>%
    dygraphs::dyOptions(
      labelsUTC = TRUE,
      drawGrid = TRUE,
      colors = "#8F733C",
      drawPoints = TRUE,
      pointSize = 2
    ) %>% 
    dygraphs::dyRangeSelector(height = 40) %>%
    dygraphs::dyCrosshair(direction = "vertical") %>%
    dygraphs::dyAxis("x",
           drawGrid = FALSE,
           gridLineColor = "#808080") %>%
    dygraphs::dyAxis("y", valueRange = c(min(as.numeric(df_plot$y)), max(as.numeric(df_plot$y))))
  
}
```

  
```{r tests-plot_serie}

#'\dontrun{
#'test_that("plot_serie works", {
#'  expect_true(inherits(plot_serie, "function")) 
#' })
#' }
```
  

```{r function-data_serie}

#' Title: data_serie
#' 
#' Description: This is an helper function to show a table with data from a BPstat serie and used from the main function ya_info_serie()
#' 
#' @param id A serie ID from the BPstat.
#' @param lng A string that represents the languages supported by BPstat API. Currently only uses "PT" or "EN". Defaults to "EN"
#' 
#' @importFrom httr2 request
#' @importFrom httr2 req_user_agent
#' @importFrom httr2 req_perform
#' @importFrom httr2 resp_status
#' @importFrom jsonlite read_json
#' @importFrom jsonlite fromJSON
#' @importFrom dplyr between
#' @importFrom dplyr tibble
#' @importFrom tidyr unnest_longer
#' @importFrom tidyr unnest_wider
#' @importFrom dplyr mutate
#' @importFrom dplyr across
#' @importFrom dplyr select
#' @importFrom htmltools tags
#' @importFrom DT datatable
#' 
#' @return A data tables with information abot the serie
#' 
#' @noRd
#' 
data_serie <- function(id, lng){
  
  basepath <- "https://bpstat.bportugal.pt"
  
  url_sv <- paste0(basepath,
                   "/api/observations/?series_ids=",
                   id)
  
  url_sfv <- paste0(basepath,
                    "/api/series/?view_full=true&page_size=1&series_ids=",
                    id)
  
  response <- httr2::request(url_sv) %>% 
    httr2::req_user_agent("YABPstat package") %>% 
    httr2::req_perform()
  
  st_c <- httr2::resp_status(response)
  
  status_description <-
    check_status_code(st_c, lng)
  
  url_sv_json <- jsonlite::read_json(url_sv)
  
  if (dplyr::between(st_c, 300, 550)) {
    stp_msg <- paste0("Estado :",
                      st_c,
                      " - ",
                      status_description,
                      ".")
    
    stop(stp_msg)
  }
  
  df_data <- url_sv_json %>%
    dplyr::tibble() %>%
    tidyr::unnest_longer(1) %>%
    tidyr::unnest_wider(1) %>%
    dplyr::mutate(dplyr::across(reference_date, as.Date),
                  dplyr::across(pub_date, as.Date)) %>%
    dplyr::select(reference_date, value, pub_date)
  
  url_sfv_json <- jsonlite::fromJSON(url_sfv)
  
  if (lng == "EN" || lng == "en") {
    column_names <-
      c("Reference date",
        "Value",
        "Updated at")
    
    capt <- paste0("YABPstat: Information about \"",
                   url_sfv_json[["data"]][["title"]][["EN"]],
                   "\"")
    
    translate_to <-
      "//cdn.datatables.net/plug-ins/1.10.11/i18n/English.json"
    
    
  } else {
    column_names <-
      c("Data refer\u00eancia",
        "Valor",
        "Atualiza\u00e7\u00e3o em")
    
    capt <- paste0("YABPstat: Informa\u00e7\u00e3o acerca \"",
                   url_sfv_json[["data"]][["title"]][["PT"]],
                   "\"")
    
    translate_to <-
      "//cdn.datatables.net/plug-ins/1.10.11/i18n/Portuguese-Brasil.json"
    
  }
  
  DT::datatable(
    data = df_data,
    extensions = "Buttons",
    style = "auto",
    class = "cell-border stripe",
    rownames = FALSE,
    colnames = column_names,
    caption = htmltools::tags$caption(style = "caption-side: top; 
                                      text-align: center; 
                                      color:black;  
                                      font-size:200% ;",
                                      capt),
    options = list(
      columnDefs = list(list(
        className = "dt-center", targets = c(1)
      )),
      searchHighlight = TRUE,
      search = list(regex = TRUE),
      order = list(list(0, "asc")),
      options = list(dom = "Bft",
                     buttons = c("csv", "excel", "pdf")),
      language = list(url = translate_to)
    )
  )
  
    
}
```
  

  
```{r tests-data_serie}
#'\dontrun{
#'test_that("data_serie works", {
#'  expect_true(inherits(data_serie, "function")) 
#'  })
#'  }
```
 

```{r function-add_favourite}
#'
#' Title: add_favourite()
#' 
#' Description: This is an helper function that adds series ID from BPstat to users favourites.
#' 
#' @param id A serie ID from the BPstat.
#' @param dataset A dataset corresponding to users favourites
#' 
#' @importFrom httr2 request
#' @importFrom httr2 req_user_agent
#' @importFrom httr2 req_perform
#' @importFrom httr2 resp_status
#' @importFrom dplyr between
#' @importFrom dplyr %>%
#' 
#' @return A success message from a well succeed insertion of a new serie.
#' 
#' @noRd
#' 
add_favourite <- function(id, dataset){
  
  basepath_url <- "https://bpstat.bportugal.pt"
  
  url <- paste0(basepath_url,
           "/api/series/?view_full=true&series_ids=",
           id)

  if (!is.numeric(id)) {
    stop("Wrong data type in \"series_id\" input.")

  }  

  response <- httr2::request(url) %>% 
    httr2::req_user_agent("YABPstat package") %>% 
    httr2::req_perform()

  st_c <- httr2::resp_status(response)
  
  status_description <-
    check_status_code(st_c, lang)
  
  if (dplyr::between(st_c, 300, 550)) {
    stp_msg <- paste0("Estado :",
                      st_c,
                      " - ",
                      status_description,
                      ".")
    
    stop(stp_msg)
  }
  
  dataset[nrow(dataset) + 1,] <- id
  
  dataset <- dataset %>%
    unique()
  
  return(save_output(r_object = dataset,
                    file_directory = "datasets",
                    file_name = "YABPstat_favourites",
                    extension = rds))
  
  message("Record added with success.")
    
}
```
  

  
```{r tests-add_favourite}
#'\dontrun{
# test_that("add_favourite works", {
#   expect_true(inherits(add_favourite, "function")) 
#'})
#'}
#'
```
  

```{r function-delete_favourite}
#'
#' Title: delete_favourite
#' 
#' Description: This is an helper function that delete BPstat series ID from users favourites.
#' 
#' @param id A serie ID from the BPstat.
#' @param dataset A dataset corresponding to users favourites
#' 
#' @importFrom httr2 request
#' @importFrom httr2 req_user_agent
#' @importFrom httr2 req_perform
#' @importFrom httr2 resp_status
#' @importFrom dplyr between
#' @importFrom dplyr %>%
#' 
#' @return A success message from a well succeed deletion of a serie.
#' 
#' @noRd
#' 
delete_favourite <- function(id, dataset){
  
  basepath_url <- "https://bpstat.bportugal.pt"
  
  url <- paste0(basepath_url,
           "/api/series/?view_full=true&series_ids=",
           id)

  #check if series_id is numeric
  if (!is.numeric(id)) {
    stop("Wrong data type in \"series_id\" input.")
    
  }
  
  response <- httr2::request(url) %>% 
    httr2::req_user_agent("YABPstat package") %>% 
    httr2::req_perform()
  
  st_c <- httr2::resp_status(response)
  
  status_description <-
    check_status_code(st_c, lang)
  
  if (dplyr::between(st_c, 300, 550)) {
    stp_msg <- paste0("Estado :",
                      st_c,
                      " - ",
                      status_description,
                      ".")
    
    stop(stp_msg)
  }
  
  if (nrow(dataset) == 0) {
    stop("Attention: there is no record to delete.")
  }
  
  dataset <- subset(dataset, dataset$series_id == id)
  
  return(
    saveRDS(object = dataset,
            file = "ya_favourites.rds")
  )
  
  message("Record deleted with success.")
    
}
```
  

  
```{r tests-delete_favourite}
#'\dontrun{
# test_that("delete_favourite works", {
#   expect_true(inherits(delete_favourite, "function")) 
# })
#'}
```
   

# ya_api_info()

Shows useful informations about BPstat API.
    
```{r function-ya_api_info}

#' Title: ya_api_info()
#' 
#' Description: Shows useful informations such as type, status code and description, and version of current BPstat Data API.
#' 
#' @param lang  A string that represents the languages supported by BPstat API. Currently only uses "PT" or "EN". Defaults to "EN"
#' 
#' @importFrom httr2 request
#' @importFrom httr2 req_user_agent
#' @importFrom httr2 req_perform
#' @importFrom httr2 resp_status
#' @importFrom jsonlite fromJSON
#' @importFrom dplyr %>%
#' 
#' @return  A string with type, status code and description, and api version in Portuguese an English languages, and a generalized error message to check internet connection.
#' 
#' @export
#' 
ya_api_info <- function(lang = "EN") {
  
  lang <- "PT"
  
  check_language(lang)
  
  basepath_url <- "https://bpstat.bportugal.pt"
  
  url <- paste(basepath_url,
                      "/data/docs/?format=openapi",
                      sep = "")
  
  tryCatch({
    
    response <- httr2::request(url) %>% 
      httr2::req_user_agent("YABPstat package") %>% 
      httr2::req_perform()
    
    type <- response %>% 
      httr2::resp_content_type()    

    api_version <-
      check_api_version(jsonlite::fromJSON(url))

    st_c <- httr2::resp_status(response)

    status_description <-
      check_status_code(st_c, lang)
    
    if (lang == "EN" || lang == "en") {
      if (api_version == "v1") {
        msg_api <- paste0(
          "API type: ",
          type,
          ".\n",
          "Status: ",
          st_c,
          " - ",
          status_description,
          "\n",
          "API version: ",
          api_version,
          "."
        )
        
        message(msg_api)
        
      } else {
        msg_api <- paste0(
          "API type: ",
          type,
          ".\n",
          "Status: ",
          st_c,
          " - ",
          status_description,
          "\n",
          "API version not supported: ",
          api_version,
          "."
        ) 
        warning(msg_api)
        
      }
      
    } else if (lang == "PT" || lang == "pt") {
      if (api_version == "v1") {
        msg_api <- paste0(
          "Tipo da API: ",
          type,
          ".\n",
          "Estado: ",
          st_c,
          " - ",
          status_description,
          "\n",
          "\u0056\u0065\u0072\u0073\u00e3\u006f da API: ",
          api_version,
          "."
        )
        
        message(msg_api)
        
      } else {
        msg_api <- paste0(
          "Tipo da API: ",
          type,
          ".\n",
          "Estado: ",
          st_c,
          " - ",
          status_description,
          "\n",
          "\u0056\u0065\u0072\u0073\u00e3\u006f da API \u006e\u00e3\u006f suportada: ",
          api_version,
          "."
        )
        
        warning(msg_api)
        
      }
      
    }
    
  }, error = function(e) {
    if (lang == "EN" || lang == "en") {
      err_msg <- paste0("Error: ",
                        "\n",
                        "Something went wrong. Please contact the maintainer.")
      
    } else {
      err_msg <- paste0("Erro: ",
                        "\n",
                        "Aconteceu um erro inesperado. Por favor entre em contacto com a equipa de desenvolvimento.")
      
    }
    stop(err_msg)
    
  })
  
}

```
  
```{r example-ya_api_info}
ya_api_info()
```
  
```{r tests-ya_api_info}
#'\dontrun{
#' test_that("ya_api_info works", {
#'   expect_message(ya_api_info(lang="PT"))
#'   expect_error(ya_api_info(lang="FR")) 
#' })
#'}
```



# ya_get_domain()

This function gathers information about BPstat domains located at "https://bpstat.bportugal.pt/data/v1/domains/?lang=PT" or "https://bpstat.bportugal.pt/data/v1/domains/?lang=EN"
    
```{r function-ya_get_domain}

#' Title: ya_get_domain()
#' 
#' Description: This function gathers information about BPstat domains and makes visible to the user in a table format for better visualization and comprehension. The returned fields are: 
#' ID - The unique ID of the domain in the BPstat structure and identification.
#' Parent ID - The ID of the parent section (none if it is a top level domain)
#' Order - The order where it is displayed in the BPstat theme organization
#' Label - The label of the domain
#' Short label - Short label of the domain 
#' Description - The domain description
#' Has series - If the domain has series (True if it has, False if it has not)
#' Last update - Last date when the domain has been updated
#' Number of series - Number of series that the domain has
#' Number of datasets - Number of datasets that the domain has
#' Domain URL - The Uniform Resource Location of the domain in BPstat
#' Dataset URL - The Uniform Resource Location of the dataset in BPstat
#' Dimension URL - The Uniform Resource Location of the dimension in BPstat
#' 
#' @param lang A string that represents the languages supported by BPstat API. Currently only uses "PT" or "EN". Defaults to "EN"
#' 
#' @importFrom httr2 request
#' @importFrom httr2 req_user_agent
#' @importFrom httr2 req_perform
#' @importFrom httr2 resp_status
#' @importFrom httr2 resp_body_raw
#' @importFrom jsonlite fromJSON
#' @importFrom dplyr between
#' @importFrom dplyr %>%
#' @importFrom dplyr tibble
#' @importFrom DT datatable
#' @importFrom htmltools tag
#' 
#' @return A DT table in the RStudio viewer
#' 
#' @export
#' 
ya_get_domain <- function(lang = "EN"){
  
  check_language(lang)
  
  temp_df <- dplyr::tibble()
  
  basepath_url <- "https://bpstat.bportugal.pt"
  
  url <- paste0(basepath_url,
              "/data/v1/domains/?lang=",
              toupper(lang))
  
  tryCatch({
    
    response <- httr2::request(url) %>% 
      httr2::req_user_agent("YABPstat package") %>% 
      httr2::req_perform()
    
    st_c <- httr2::resp_status(response)

    status_description <-
      check_status_code(st_c, lang)
    
    if (dplyr::between(st_c, 400, 550)) {
      stp_msg <- paste0("Estado :",
                        st_c,
                        " - ",
                        status_description,
                        ".")
      
      stop(stp_msg)
      
    } else {
      raw_response <- httr2::resp_body_raw(response)
    
      temp_df <- jsonlite::fromJSON(rawToChar(raw_response))
      
      if (lang == "EN" || lang == "en") {
        column_names <- c(
          "ID",
          'Parent ID',
          'Order',
          'Label',
          'Short label',
          'Description',
          'Has series',
          'Last update',
          'Number of series',
          'Number of datasets',
          'Domain URL',
          'Dataset URL',
          'Dimension URL'
        )
        
        capt <- "YABPstat: List of domains"
        
        translate_to <-
          '//cdn.datatables.net/plug-ins/1.10.11/i18n/English.json'
        
      } else if (lang == "PT" || lang == "pt") {
        column_names <- c(
          "ID",
          'N\u00f3 pai',
          'Ordem',
          'Etiqueta',
          'Abreviatura',
          'Descri\u00e7\u00e3o',
          'Tem s\u00e9ries',
          'Ultima atualiza\u00e7\u00e3o',
          'N\u00famero de s\u00e9ries',
          'N\u00famero de datasets',
          'URL do dom\u00ednio',
          'URL do dataset',
          'URL da dimens\u00e3o'
        )
        
        capt <- "YABPstat: Lista de dominios"
        
        translate_to <-
          '//cdn.datatables.net/plug-ins/1.10.11/i18n/Portuguese-Brasil.json'
        
      } else {
        err_msg <- paste0("O idioma ainda n\u00e3o \u00e9 suportado.",
                          "\n",
                          "Por favor escolha entre \"EN\" ou \"PT\".")
        stop(err_msg)
        
      }
      
      DT::datatable(
        data = temp_df,
        style = "auto",
        class = "cell-border stripe",
        caption = htmltools::tags$caption(
          style = "caption-side: top;
                  text-align: center;
                  color:black;  font-size:200% ;
                  padding-top: 20px;
                  padding-bottom: 15px;",
          capt
        ),
        rownames = FALSE,
        colnames = column_names,
        options = list(
          columnDefs = list(list(
            className = 'dt-center', targets = c(0:12)
          )),
          searchHighlight = TRUE,
          search = list(regex = TRUE),
          language = list(url = translate_to)
        )
      )
    }
    
    
  }, error = function(e) {
    if (lang == "EN" || lang == "en") {
      err_msg <- paste0("Error: ",
                        "\n",
                        "Something went wrong. Please contact the maintainer.")
      
    } else {
      err_msg <- paste0("Erro: ",
                        "\n",
                        "Aconteceu um erro inesperado. Por favor entre em contacto com a equipa de desenvolvimento.")
      
    }
    stop(err_msg)
    
  })
  
    
}

```
  
```{r example-ya_get_domain}
ya_get_domain()
```
  
```{r tests-ya_get_domain}
#\dontrun{
# test_that("ya_get_domain works", {
#   expect_true(ya_get_domain(lang = "PT")) 
#   expect_error(ya_get_domain(lang = "ES"))
# })
#}
```
  

# ya_save_domain()

This function allows saving the information about BPstat domains to an external file.
    
```{r function-ya_save_domain}

#' Title: ya_save_domain()
#' 
#' Description: A function that saves de information avaliable about the BPstat domains
#' 
#' @param lang  A string that represents the languages supported by BPstat API. Currently only uses "PT" or "EN". Defaults to "EN"
#' @param extension A string that represents the avaliable extensions to save files. Currently only uses "rds" or "csv". Defaults to "rds"
#' 
#' @importFrom httr2 request
#' @importFrom httr2 req_user_agent
#' @importFrom httr2 req_perform
#' @importFrom httr2 resp_status
#' @importFrom httr2 resp_body_raw
#' @importFrom dplyr between
#' @importFrom dplyr %>%
#' @importFrom jsonlite fromJSON
#' 
#' @return A file with the available data from the domains in the rds or csv format.
#' 
#' @export
#' 
ya_save_domain <- function(lang = "EN", extension = "rds"){
  
  check_language(lang)
  
  check_extension(extension)

  basepath_url <- "https://bpstat.bportugal.pt"
  
  url <- paste0(basepath_url,
                "/data/v1/domains/?lang=",
                toupper(lang))
  
  response <- httr2::request(url) %>% 
    httr2::req_user_agent("YABPstat package") %>% 
    httr2::req_perform()
  
  st_c <- httr2::resp_status(response)
  
  status_description <-
    check_status_code(st_c, lang)
  
  if (dplyr::between(st_c, 400, 550)) {
    stp_msg <- paste0("Estado :",
                      st_c,
                      " - ",
                      status_description,
                      ".")
    
    stop(stp_msg)
    
  } else {
    
    raw_response <- httr2::resp_body_raw(response)
    
    temp_df <- jsonlite::fromJSON(rawToChar(raw_response))
    
    return(
      save_output(
        r_object = temp_df,
        file_directory = "raw",
        file_name = "bpstat_domains",
        extension = extension
      )
    )
  }
    
}

```
  
```{r example-ya_save_domain}
ya_save_domain()
```
  
```{r tests-ya_save_domain}
#' \dontrun{
#' test_that("ya_save_domain works", {
#'   expect_true(ya_save_domain()) 
#' })
#' }
```
  

# ya_get_dataset()

This function gathers information about BPstat domains located at "https://bpstat.bportugal.pt/data/v1/domains/{domain_id}/datasets/?lang=PT&page_size=100" or "https://bpstat.bportugal.pt/data/v1/domains/{domain_id}/datasets/?lang=EN&page_size=100"
    
```{r function-ya_get_dataset}

#' Title: ya_get_dataset()
#' 
#' Description: Gathers information about the datasets in BPstat.
#' 
#' @param lang  A string that represents the languages supported by BPstat API. Currently only uses "PT" or "EN". Defaults to "EN"
#' 
#' @importFrom httr2 request
#' @importFrom httr2 req_user_agent
#' @importFrom httr2 req_perform
#' @importFrom httr2 resp_status
#' @importFrom httr2 resp_body_raw
#' @importFrom jsonlite fromJSON
#' @importFrom dplyr between
#' @importFrom dplyr select
#' @importFrom dplyr %>%
#' @importFrom dplyr tibble
#' @importFrom tidyr drop_na
#' @importFrom DT datatable
#' @importFrom htmltools tags
#' 
#' @return A data table with the information about the BPstat domains
#' 
#' @export
#' 
ya_get_dataset <- function(lang = "EN"){

  check_language(lang)
  
  temp_df <- dplyr::tibble()
  
  basepath_url <- "https://bpstat.bportugal.pt"
  
  url <- paste0(basepath_url,
                "/data/v1/domains/?lang=",
                toupper(lang))
  
  tryCatch({
    
    response <- httr2::request(url) %>%
      httr2::req_user_agent("YABPstat package") %>%
      httr2::req_perform()
    
    st_c <- httr2::resp_status(response)
    
    status_description <-
      check_status_code(st_c, lang)
    
    if (dplyr::between(st_c, 400, 550)) {
      stp_msg <- paste0("Estado :",
                        st_c,
                        " - ",
                        status_description,
                        ".")
      
      stop(stp_msg)
      
    } else {
      raw_response <- httr2::resp_body_raw(response)
      
      temp_df <- jsonlite::fromJSON(rawToChar(raw_response))
      
      temp_df <- temp_df %>%
        dplyr::select(datasets_href, num_datasets) %>%
        tidyr::drop_na()
      
      
      if (lang == "EN" || lang == "en") {
        column_names <- c('Dataset URL', '\u0023 of datasets')
        
        capt <- "YABPstat: Datasets per domain"
        
        translate_to <-
          '//cdn.datatables.net/plug-ins/1.10.11/i18n/English.json'
        
      } else {
        column_names <- c('URL do dataset', 'N\u00famero de datasets')
        
        capt <- "YABPstat: Datasets por dom\u00ednio"
        
        translate_to <-
          '//cdn.datatables.net/plug-ins/1.10.11/i18n/Portuguese-Brasil.json'
        
      }
      
      DT::datatable(
        data = temp_df,
        style = "auto",
        class = "cell-border stripe",
        caption = htmltools::tags$caption(
          style = "caption-side: top;
                text-align: center;
                color:black;  font-size:200% ;
                padding-top: 20px;
                padding-bottom: 15px;",
          capt
        ),
        rownames = FALSE,
        colnames = column_names,
        options = list(
          columnDefs = list(list(
            className = 'dt-center', targets = c(1)
          )),
          searchHighlight = TRUE,
          search = list(regex = TRUE),
          language = list(url = translate_to)
        )
      )
    }
    
  }, error = function(e) {
    if (lang == "EN" || lang == "en") {
      err_msg <- paste0("Error: ",
                        "\n",
                        "Please check your internet connection.")
      
    } else {
      err_msg <- paste0("Erro: ",
                        "\n",
                        "Por favor verifique a sua liga\u00e7\u00e3o \u00e0 internet.")
      
    }
    stop(err_msg)
    
  })
  
}

```
  
```{r example-ya_get_dataset}
ya_get_dataset()
```
  
```{r tests-ya_get_dataset}
#' \dontrun{
#' test_that("ya_get_dataset works", {
#'  expect_true(ya_get_dataset()) 
#'})
#'}

```


# ya_save_dataset()

This function allows saving the information about BPstat datasets to an external file.
    
```{r function-ya_save_dataset}

#' Title ya_save_dataset()
#' 
#' Description A function that saves de information avaliable about the BPstat datasets
#' 
#' @param lang  A string that represents the languages supported by BPstat API. Currently only uses "PT" or "EN". Defaults to "EN"
#' @param extension A string that represents the avaliable extensions to save files. Currently only uses "rds" or "csv". Defaults to "rds"
#' 
#' @importFrom httr2 request
#' @importFrom httr2 req_user_agent
#' @importFrom httr2 req_perform
#' @importFrom httr2 resp_status
#' @importFrom httr2 resp_body_raw
#' @importFrom dplyr %>%
#' @importFrom dplyr between
#' @importFrom dplyr select
#' @importFrom tidyr drop_na
#' @importFrom jsonlite fromJSON
#' 
#' @return A file with the information about BPstat datasets with the rds or csv extension.
#' 
#' @export
#' 
ya_save_dataset <- function(lang = "EN", extension = "rds"){

  check_language(lang)
  
  check_extension(extension)
  
  basepath_url <- "https://bpstat.bportugal.pt"
  
  url <- paste0(basepath_url,
                "/data/v1/domains/?lang=",
                toupper(lang))
  
  response <- httr2::request(url) %>% 
    httr2::req_user_agent("YABPstat package") %>% 
    httr2::req_perform()
  
  st_c <- httr2::resp_status(response)
  
  status_description <-
    check_status_code(st_c, lang)
  
  if (dplyr::between(st_c, 400, 550)) {
    stp_msg <- paste0("Estado :",
                      st_c,
                      " - ",
                      status_description,
                      ".")
    
    stop(stp_msg)
    
  } else {
    raw_response <- httr2::resp_body_raw(response)
    
    temp_df <- jsonlite::fromJSON(rawToChar(raw_response))
    
    temp_df <- temp_df %>%
      dplyr::select(datasets_href, num_datasets) %>%
      tidyr::drop_na()
    
    return(
      save_output(
        r_object = temp_df,
        file_directory = "raw",
        file_name = "bpstat_dataset",
        extension = extension
      )
    )
  }
  
}

```
  
```{r example-ya_save_dataset}
ya_save_dataset()
```
  
```{r tests-ya_save_dataset}
#' \dontrun{
#'test_that("ya_save_dataset works", {
#'  expect_true(ya_save_dataset()) 
#'})
#'}

```


# ya_get_dataset_item()

Gathers information available in BPstat about the dataset items.
    
```{r function-ya_get_dataset_item}

#' Title: ya_get_dataset_item()
#' 
#' Description: A function that gathers information available in BPstat about the dataset items.
#' 
#' @param lang  A string that represents the languages supported by BPstat API. Currently only uses "PT" or "EN". Defaults to "EN"
#' 
#' @importFrom httr2 request
#' @importFrom httr2 req_user_agent
#' @importFrom httr2 req_perform
#' @importFrom httr2 resp_status
#' @importFrom httr2 resp_body_raw
#' @importFrom dplyr between
#' @importFrom dplyr select
#' @importFrom dplyr tibble
#' @importFrom dplyr %>%
#' @importFrom tidyr drop_na
#' @importFrom jsonlite fromJSON
#' @importFrom htmltools tags
#' @importFrom DT datatable
#' 
#' @return A data table with the information in a more human readable form with a search option using regex.
#' 
#' @export
#' 
ya_get_dataset_item <- function(lang = "EN"){

  check_language(lang)
  
  tmp_dset_df <- dplyr::tibble()
  
  temp_df <- dplyr::tibble()
  
  basepath_url <- "https://bpstat.bportugal.pt"
  
  url <- paste0(basepath_url,
                "/data/v1/domains/?lang=",
                toupper(lang))
  
  tryCatch({
    
    response <- httr2::request(url) %>% 
      httr2::req_user_agent("YABPstat package") %>% 
      httr2::req_perform()

    
    st_c <- httr2::resp_status(response)
    
    status_description <-
      check_status_code(st_c, lang)
    
    if (dplyr::between(st_c, 300, 550)) {
      stp_msg <- paste0("Estado :",
                        st_c,
                        " - ",
                        status_description,
                        ".")
      
      stop(stp_msg)
      
    } else {
      
      raw_response <- httr2::resp_body_raw(response)
      
      temp_df <- jsonlite::fromJSON(rawToChar(raw_response))
      
      temp_df <- temp_df %>%
        dplyr::select(datasets_href, num_datasets) %>%
        tidyr::drop_na()
      
      
      if (lang == "EN" || lang == "en") {
        column_names <- c('Label',
                          'Dataset URL',
                          "Extension ID",
                          "\u0023 of series",
                          'Last update')
        
        capt <-
          "YABPstat: Information about datasets"
        
        translate_to <-
          '//cdn.datatables.net/plug-ins/1.10.11/i18n/English.json'
        
      } else {
        column_names <- c(
          "Etiqueta",
          'URL do dataset',
          'N\u00famero de datasets',
          "N\u00famero de s\u00e9ries",
          "Ultima atualiza\u00e7\u00e3o"
        )
        
        capt <-
          "YABPstat: Informa\u00e7\u00e3o acerca dos datasets"
        
        translate_to <-
          '//cdn.datatables.net/plug-ins/1.10.11/i18n/Portuguese-Brasil.json'
        
      }

      for (row in 1:nrow(temp_df)) {

        tmp_dset_df <- rbind(tmp_dset_df,
                             generate_datasets(temp_df$datasets_href[[row]]))
        
      }
      
      tmp_dset_df <-
        tmp_dset_df %>% dplyr::select(label,
                                      href,
                                      extension.id,
                                      extension.num_series,
                                      extension.obs_updated_at)
      
      DT::datatable(
        data = tmp_dset_df,
        style = "auto",
        class = "cell-border stripe",
        caption = htmltools::tags$caption(
          style = "caption-side: top;
                  text-align: center;
                  color:black;  font-size:200% ;
                  padding-top: 20px;
                  padding-bottom: 15px;",
          capt
        ),
        rownames = FALSE,
        colnames = column_names,
        options = list(
          columnDefs = list(list(
            className = 'dt-center', targets = c(3)
          )),
          searchHighlight = TRUE,
          search = list(regex = TRUE),
          language = list(url = translate_to)
        )
      )
    }
  }, error = function(e) {
    if (lang == "EN" || lang == "en") {
      err_msg <- paste0("Error: ",
                        "\n",
                        "Something went wrong. Please contact the maintainer.")
      
    } else {
      err_msg <- paste0("Erro: ",
                        "\n",
                        "Aconteceu um erro inesperado. Por favor entre em contacto com a equipa de desenvolvimento.")
      
    }
    stop(err_msg)
    
  })

}

```
  
```{r example-ya_get_dataset_item}
ya_get_dataset_item()
```
  
```{r tests-ya_get_dataset_item}
#'\dontrun{
#'test_that("ya_get_dataset_item works", {
#'  expect_true(inherits(ya_get_dataset_item, "function")) 
#'})
#'}
#'
```
    

# ya_save_dataset_item()

This function allows saving the information about BPstat datasets items to an external file.
    
```{r function-ya_save_dataset_item}

#' Title: ya_save_dataset_item()
#' 
#' Description: A function that saves de information available about the BPstat datasets
#' 
#' @param lang  A string that represents the languages supported by BPstat API. Currently only uses "PT" or "EN". Defaults to "EN"
#' @param extension A string that represents the available extensions to save files. Currently only uses "rds" or "csv". Defaults to "rds"
#' 
#' @importFrom httr2 request
#' @importFrom httr2 req_user_agent
#' @importFrom httr2 req_perform
#' @importFrom httr2 resp_status
#' @importFrom httr2 resp_body_raw
#' @importFrom dplyr between
#' @importFrom dplyr tibble
#' @importFrom dplyr %>%
#' @importFrom jsonlite fromJSON
#' @importFrom tidyr drop_na
#' 
#' @return A file with the information about BPstat dataset items with the rds or csv extension.
#' 
#' @export
#' 
ya_save_dataset_item <- function(lang = "EN", extension = "rds"){

  check_language(lang)
  
  check_extension(extension)
  
  tmp_dset_df <- dplyr::tibble()
  
  basepath_url <- "https://bpstat.bportugal.pt"
  
  url <- paste0(basepath_url,
                "/data/v1/domains/?lang=",
                toupper(lang))
  
  response <- httr2::request(url) %>% 
    httr2::req_user_agent("YABPstat package") %>% 
    httr2::req_perform()
  
  st_c <- httr2::resp_status(response)
  
  status_description <-
    check_status_code(st_c, lang)
  
  if (dplyr::between(st_c, 400, 550)) {
    stp_msg <- paste0("Estado :",
                      st_c,
                      " - ",
                      status_description,
                      ".")
    
    stop(stp_msg)
    
  } else {
    raw_response <- httr2::resp_body_raw(response)
    
    temp_df <- jsonlite::fromJSON(rawToChar(raw_response))
    
    temp_df <- temp_df %>%
      dplyr::select(datasets_href, num_datasets) %>%
      tidyr::drop_na()
    
    for (row in 1:nrow(temp_df)) {
      tmp_dset_df <- rbind(tmp_dset_df,
                           generate_datasets(temp_df$datasets_href[[row]]))
      
    }
    
    tmp_dset_df <- tmp_dset_df %>% 
      dplyr::select(label,
                   href,
                   extension.id,
                   extension.num_series,
                   extension.obs_updated_at)
    
    return(
      save_output(
        r_object = tmp_dset_df,
        file_directory = "raw",
        file_name = "bpstat_dataset_item",
        extension = extension
      )
    )
  }
  
}

```
  
```{r example-ya_save_dataset_item}
ya_save_dataset_item()
```
  
```{r tests-ya_save_dataset_item}
#'\dontrun{
#'test_that("ya_save_dataset_item works", {
#'  expect_true(inherits(ya_save_dataset_item, "function")) 
#'})
#'}

```
  

# ya_get_dimension()

This function gathers information about BPstat domains located at "https://bpstat.bportugal.pt/data/v1/domains/?lang=" [PT || EN]
    
```{r function-ya_get_dimension}

#' Title: ya_get_dimension()
#' 
#' Description: A function gathers information about BPstat domains located at "https://bpstat.bportugal.pt/data/v1/domains/?lang=" ("PT" or "EN")
#' 
#' @param lang  A string that represents the languages supported by BPstat API. Currently only uses "PT" or "EN". Defaults to "EN"
#' 
#' @importFrom httr2 request
#' @importFrom httr2 req_user_agent
#' @importFrom httr2 req_perform
#' @importFrom httr2 resp_status
#' @importFrom httr2 resp_body_raw
#' @importFrom dplyr between
#' @importFrom dplyr select
#' @importFrom dplyr tibble
#' @importFrom dplyr %>%
#' @importFrom tidyr drop_na
#' @importFrom jsonlite fromJSON
#' @importFrom DT datatable
#' @importFrom htmltools tags
#' 
#' @return A DT datatable in RStudio viewer pane
#' 
#' @export
#' 
ya_get_dimension <- function(lang = "EN"){

  check_language(lang)
  
  temp_df <- dplyr::tibble()
  
  basepath_url <- "https://bpstat.bportugal.pt"
  
  url <- paste0(basepath_url,
                "/data/v1/domains/?lang=",
                toupper(lang))
  
  tryCatch({
    response <- httr2::request(url) %>% 
      httr2::req_user_agent("YABPstat package") %>% 
      httr2::req_perform()
    
    
    st_c <- httr2::resp_status(response)
    
    status_description <-
      check_status_code(st_c, lang)
    
    if (dplyr::between(st_c, 300, 550)) {
      stp_msg <- paste0("Estado :",
                        st_c,
                        " - ",
                        status_description,
                        ".")
      
      stop(stp_msg)
      
    } else {
      raw_response <- httr2::resp_body_raw(response)
      
      temp_df <- jsonlite::fromJSON(rawToChar(raw_response))
      
      temp_df <- temp_df %>%
        dplyr::select(dimensions_href, num_series) %>%
        tidyr::drop_na()
      
      
      if (lang == "EN" || lang == "en") {
        column_names <- c('Dimension URL', '\u0023 of series')
        
        capt <- "YABPstat: List of dimensions"
        
        translate_to <-
          '//cdn.datatables.net/plug-ins/1.10.11/i18n/English.json'
        
      } else {
        column_names <- c('URL da dimens\u00e3o', 'N\u00famero de s\u00e9ries')
        
        capt <- "YABPstat: Lista de dimens\u00f5es"
        
        translate_to <-
          '//cdn.datatables.net/plug-ins/1.10.11/i18n/Portuguese-Brasil.json'
        
      }
      
      DT::datatable(
        data = temp_df,
        style = "auto",
        class = "cell-border stripe",
        caption = htmltools::tags$caption(
          style = "caption-side: top;
                  text-align: center;
                  color:black;  font-size:200% ;
                  padding-top: 20px;
                  padding-bottom: 15px;",
          capt
        ),
        rownames = FALSE,
        colnames = column_names,
        options = list(
          columnDefs = list(list(
            className = 'dt-center', targets = c(1)
          )),
          searchHighlight = TRUE,
          search = list(regex = TRUE),
          language = list(url = translate_to)
        )
      )
    }
  }, error = function(e) {
    if (lang == "EN" || lang == "en") {
      err_msg <- paste0("Error: ",
                        "\n",
                        "Something went wrong. Please contact the maintainer.")
      
    } else {
      err_msg <- paste0("Erro: ",
                        "\n",
                        "Aconteceu um erro inesperado. Por favor entre em contacto com a equipa de desenvolvimento.")
      
    }
    stop(err_msg)
    
  })
  
}

```
  
```{r example-ya_get_dimension}
ya_get_dimension()
```
  
```{r tests-ya_get_dimension}
#'\dontrun{
#'test_that("ya_get_dimension works", {
#'  expect_true(inherits(ya_get_dimension, "function")) 
#'})
#'}

```
  

# ya_save_dimension()

This function allows saving the information about BPstat dimensions to an external file.
    
```{r function-ya_save_dimension}

#' Title: ya_save_dimension()
#' 
#' Description: A function that saves de information available about the BPstat dimensions.
#' 
#' @param lang  A string that represents the languages supported by BPstat API. Currently only uses "PT" or "EN". Defaults to "EN"
#' @param extension A string that represents the available extensions to save files. Currently only uses "rds" or "csv". Defaults to "rds"
#' 
#' @importFrom httr2 request
#' @importFrom httr2 req_user_agent
#' @importFrom httr2 req_perform
#' @importFrom httr2 resp_status
#' @importFrom httr2 resp_body_raw
#' @importFrom dplyr between
#' @importFrom dplyr tibble
#' @importFrom dplyr %>%
#' @importFrom jsonlite fromJSON
#' @importFrom tidyr drop_na
#' 
#' @return A file with the information about BPstat dimensions with the rds or csv extension.
#' 
#' @export
#' 
ya_save_dimension <- function(lang = "EN", extension = "rds"){
  
  check_language(lang)
  
  check_extension(extension)
  
  temp_df <- dplyr::tibble()
  
  basepath_url <- "https://bpstat.bportugal.pt"
  
  url <- paste0(basepath_url,
                "/data/v1/domains/?lang=",
                toupper(lang))
  
  response <- httr2::request(url) %>%
    httr2::req_user_agent("YABPstat package") %>% 
    httr2::req_perform()

  
  st_c <- httr2::resp_status(response)
  
  status_description <-
    check_status_code(st_c, lang)
  
  if (dplyr::between(st_c, 400, 550)) {
    stp_msg <- paste0("Estado :",
                      st_c,
                      " - ",
                      status_description,
                      ".")
    
    stop(stp_msg)
    
    
  } else {
    raw_response <- httr2::resp_body_raw(response)
    
    temp_df <- jsonlite::fromJSON(rawToChar(raw_response))
    
    temp_df <- temp_df %>%
      dplyr::select(dimensions_href, num_series) %>%
      tidyr::drop_na()
    
    return(
      save_output(
        r_object = temp_df,
        file_directory = "raw",
        file_name = "bpstat_dimension",
        extension = extension
      )
    )
  }
    
}

```
  
```{r example-ya_save_dimension}
ya_save_dimension()
```
  
```{r tests-ya_save_dimension}
#'\dontrun{
# test_that("ya_save_dimension works", {
#   expect_true(inherits(ya_save_dimension, "function")) 
# })
#'}
```
  

# ya_get_dimension_item()

Gathers information avaliable in BPstat about the dimension items.
    
```{r function-ya_get_dimension_item}

#' Title: ya_get_dimension_item()
#' 
#' Description: A function that gathers information available in BPstat about the dataset items.
#' 
#' @param lang  A string that represents the languages supported by BPstat API. Currently only uses "PT" or "EN". Defaults to "EN"
#' 
#' @importFrom httr2 request
#' @importFrom httr2 req_user_agent
#' @importFrom httr2 req_perform
#' @importFrom httr2 resp_status
#' @importFrom httr2 resp_body_raw
#' @importFrom dplyr between
#' @importFrom dplyr select
#' @importFrom dplyr tibble
#' @importFrom dplyr %>%
#' @importFrom tidyr drop_na
#' @importFrom jsonlite fromJSON
#' @importFrom htmltools tags
#' @importFrom DT datatable
#' 
#' @return A data table with the information in a more human readable form with a search option using regex.
#' 
#' @export
#' 
ya_get_dimension_item <- function(lang = "EN"){
  
  check_language(lang)
  
  tmp_dset_df <- dplyr::tibble()
  
  temp_df <- dplyr::tibble()
  
  basepath_url <- "https://bpstat.bportugal.pt"
  
  url <- paste0(basepath_url,
                "/data/v1/domains/?lang=",
                toupper(lang))
  
  tryCatch({
    
    response <- httr2::request(url) %>% 
      httr2::req_user_agent("YABPstat package") %>% 
      httr2::req_perform()
    
    st_c <- httr2::resp_status(response)
    
    status_description <-
      check_status_code(st_c, lang)
    
    if (dplyr::between(st_c, 300, 550)) {
      stp_msg <- paste0("Estado :",
                        st_c,
                        " - ",
                        status_description,
                        ".")
      
      stop(stp_msg)
      
      
    } else {
      
      raw_response <- httr2::resp_body_raw(response)
      
      temp_df <- jsonlite::fromJSON(rawToChar(raw_response))
      
      temp_df <- temp_df %>%
        dplyr::select(dimensions_href, num_series) %>%
        tidyr::drop_na()
      
      if (lang == "EN" || lang == "en") {
        column_names <- c('Description', "Item label", "Item URL")
        
        capt <-
          "YABPstat: Information about dimensions"
        
        translate_to <-
          '//cdn.datatables.net/plug-ins/1.10.11/i18n/English.json'
        
      } else {
        column_names <- c("Descri\u00e7\u00e3o", "Item", "URL do item")
        
        capt <-
          "YABPstat: Informa\u00e7\u00e3o acerca das dimens\u00f5es"
        
        translate_to <-
          '//cdn.datatables.net/plug-ins/1.10.11/i18n/Portuguese-Brasil.json'
        
      }
      
      for (row in 1:nrow(temp_df)) {
        tmp_dset_df <- rbind(tmp_dset_df,
                             generate_dimensions(temp_df$dimensions_href[[row]]))
      }
      
      
      tmp_dset_df <-
        tmp_dset_df %>% dplyr::select(description,
                                      item_label,
                                      item_href)
      
      DT::datatable(
        data = tmp_dset_df,
        style = "auto",
        class = "cell-border stripe",
        caption = htmltools::tags$caption(
          style = "caption-side: top;
                  text-align: center;
                  color:black;  font-size:200% ;
                  padding-top: 20px;
                  padding-bottom: 15px;",
          capt
        ),
        rownames = FALSE,
        colnames = column_names,
        options = list(
          columnDefs = list(list(
            className = 'dt-center', targets = c()
          )),
          searchHighlight = TRUE,
          search = list(regex = TRUE),
          language = list(url = translate_to)
        )
      )
    }
  }, error = function(e) {
    if (lang == "EN" || lang == "en") {
      err_msg <- paste0("Error: ",
                        "\n",
                        "Something went wrong. Please contact the maintainer.")
      
    } else {
      err_msg <- paste0("Erro: ",
                        "\n",
                        "Aconteceu um erro inesperado. Por favor entre em contacto com a equipa de desenvolvimento.")
      
    }
    stop(err_msg)
    
  })
  
}

```
  
```{r example-ya_get_dimension_item}
ya_get_dimension_item()
```
  
```{r tests-ya_get_dimension_item}
#'\dontrun{
#'test_that("ya_get_dimension_item works", {
#'  expect_true(inherits(ya_get_dimension_item, "function")) 
#'})
#'}
```
  
  
# ya_save_dimension_item()

This function allows saving the information about BPstat dimensions items to an external file.
    
```{r function-ya_save_dimension_item}

#' Title: ya_save_dimension_item()
#' 
#' Description: A function that saves de information available about the BPstat dimensions items.
#' 
#' @param lang  A string that represents the languages supported by BPstat API. Currently only uses "PT" or "EN". Defaults to "EN"
#' @param extension A string that represents the available extensions to save files. Currently only uses "rds" or "csv". Defaults to "rds"
#' 
#' @importFrom httr2 request
#' @importFrom httr2 req_user_agent
#' @importFrom httr2 req_perform
#' @importFrom httr2 resp_status
#' @importFrom dplyr between
#' @importFrom dplyr tibble
#' @importFrom dplyr select
#' @importFrom dplyr %>%
#' @importFrom jsonlite fromJSON
#' @importFrom tidyr drop_na
#' 
#' @return A file with the information about BPstat dimensions items with the rds or csv extension.
#' 
#' @export
#' 
ya_save_dimension_item <- function(lang = "EN", extension = "rds"){
  
  check_language(lang)
  
  check_extension(extension)
  
  tmp_dset_df <- dplyr::tibble()
  
  temp_df <- dplyr::tibble()
  
  basepath_url <- "https://bpstat.bportugal.pt"
  
  url <- paste0(basepath_url,
                "/data/v1/domains/?lang=",
                toupper(lang))
  
  response <- httr2::request(url) %>% 
    httr2::req_user_agent("YABPstat package") %>% 
    httr2::req_perform()
  
  st_c <- httr2::resp_status(response)
  
  status_description <-
    check_status_code(st_c, lang)
  
  if (dplyr::between(st_c, 300, 550)) {
    stp_msg <- paste0("Estado :",
                      st_c,
                      " - ",
                      status_description,
                      ".")
    
    stop(stp_msg)
    
    
  } else {
    raw_response <- httr2::resp_body_raw(response)
    
    temp_df <- jsonlite::fromJSON(rawToChar(raw_response))
    
    temp_df <- temp_df %>%
      dplyr::select(dimensions_href, num_series) %>%
      tidyr::drop_na()
    
    for (row in 1:nrow(temp_df)) {
      tmp_dset_df <- rbind(tmp_dset_df,
                           generate_dimensions(temp_df$dimensions_href[[row]]))
    }
    
    
    tmp_dset_df <- tmp_dset_df %>% 
      dplyr::select(description,
                    item_label,
                    item_href)
    
    return(
      save_output(
        r_object = tmp_dset_df,
        file_directory = "raw",
        file_name = "bpstat_domain_item",
        extension = extension
      )
    )
  }
    
}

```
  
```{r example-ya_save_dimension_item}
ya_save_dimension_item()
```
  
```{r tests-ya_save_dimension_item}
#'\dontrun{
#'test_that("ya_save_dimension_item works", {
#'  expect_true(inherits(ya_save_dimension_item, "function")) 
#'})
#'}
```


# ya_get_dimension_description()

Gathers information avaliable in BPstat about the dimension items and description.
    
```{r function-ya_get_dimension_description}

#' Title ya_get_dimension_description()
#' 
#' Description: A function that gathers information avaliable in BPstat about the dimension items and description. This function takes a little longer to execute.
#' 
#' @param lang  A string that represents the languages supported by BPstat API. Currently only uses "PT" or "EN". Defaults to "EN"
#' 
#' @importFrom httr2 request
#' @importFrom httr2 req_user_agent
#' @importFrom httr2 req_perform
#' @importFrom httr2 resp_status
#' @importFrom httr2 resp_body_raw
#' @importFrom dplyr between
#' @importFrom dplyr select
#' @importFrom dplyr mutate
#' @importFrom dplyr filter
#' @importFrom dplyr tibble
#' @importFrom dplyr rename
#' @importFrom dplyr %>%
#' @importFrom tidyr drop_na
#' @importFrom jsonlite fromJSON
#' @importFrom DT datatable
#' @importFrom htmltools tags
#' 
#' @return A DT datatable in RStudio viewer pane
#' 
#' @export
#' 
ya_get_dimension_description <- function(lang = "EN"){
  
  check_language(lang)
  
  tmp_dset_df <- dplyr::tibble()
  
  temp_df <- dplyr::tibble()
  
  basepath_url <- "https://bpstat.bportugal.pt"
  
  url <- paste0(basepath_url,
             "/data/v1/domains/?lang=",
             toupper(lang))
  
  tryCatch({
    
    response <- httr2::request(url) %>% 
      httr2::req_user_agent("YABPstat package") %>% 
      httr2::req_perform()

    
    st_c <- httr2::resp_status(response)
    
    status_description <-
      check_status_code(st_c, lang)
    
    if (dplyr::between(st_c, 400, 550)) {
      stp_msg <- paste0("Estado :",
                        st_c,
                        " - ",
                        status_description,
                        ".")
      
      stop(stp_msg)
      
      
    } 
      
      raw_response <- httr2::resp_body_raw(response)
      
      temp_df <- jsonlite::fromJSON(rawToChar(raw_response))
      
      temp_df <- temp_df %>%
        dplyr::select(dimensions_href, num_series) %>%
        tidyr::drop_na()
      
      for (row in 1:nrow(temp_df)) {
        tmp_dset_df <- rbind(tmp_dset_df,
                             generate_dimensions(temp_df$dimensions_href[[row]]))
      }
      

      item_url_status <- function(url) {
        
        response <- httr2::request(url) %>% 
          httr2::req_user_agent("YABPstat package") %>% 
          httr2::req_error(is_error = function(response) FALSE) %>% 
          httr2::req_perform()
        
        return(response$status_code)
        
      }
      
      tmp_dset_df <- tmp_dset_df %>%
        dplyr::select(item_href) %>%
        dplyr::mutate(status = sapply(item_href, item_url_status)) %>%
        dplyr::filter(status == 200) %>%
        dplyr::select(item_href)
      
      full_df <- dplyr::tibble()
      
      for (row in 1:nrow(tmp_dset_df)) {
        
        tryCatch({
          tmp_df <- NULL
          
          get_description <-
            httr2::request(tmp_dset_df[row, ]) %>% 
            httr2::req_user_agent("YABPstat package") %>% 
            httr2::req_perform()
          
          raw_response <- httr2::resp_body_raw(get_description)
          
          contents <-
            jsonlite::fromJSON(rawToChar(raw_response))
          
          tmp_lst <-
            do.call(rbind, contents$category$label)
          
          tmp_df <- as.data.frame(tmp_lst) %>%
            dplyr::rename(value = V1)
          
          tmp_df <-
            cbind(label = rownames(tmp_df), tmp_df)
          
          rownames(tmp_df) <- 1:nrow(tmp_df)
          
          tmp_df <- tmp_df %>%
            mutate(version = contents$version,
                   category_label = contents$label,
                    href = contents$href,
                    extension_id = contents$extension$id,
                    extension_description = contents$extension$description,
                    class = contents$class,
                    source = contents$source)
          
          full_df <- rbind(full_df, tmp_df)
          
        },
        error = function(e) {
          message("Erro: \n")
          # print(e)
          row = row + 1
        })
      }
      
      if (lang == "EN" | lang == "en") {
        column_names <-
          c(
            "Label",
            "Value",
            "Version",
            "Category label",
            "Hyperlink",
            "Extension ID",
            "Extension description",
            "Class",
            "Source"
          )
        
        capt <- "YABPstat: Dimensions description"
        
        translate_to <-
          "//cdn.datatables.net/plug-ins/1.10.11/i18n/English.json"
        
      } else {
        column_names <-
          c(
            "Etiqueta",
            "Valor",
            "Vers\u00e3o",
            "Categoria",
            "Hiperliga\u00e7\u00e3o",
            "ID extens\u00e3o",
            "Descri\u00e7\u00e3o da extens\u00e3o",
            "Classe",
            "Origem"
          )
        
        capt <-
          "YABPstat: Descri\u00e7\u00e3o das dimens\u00f5es"
        
        translate_to <-
          "//cdn.datatables.net/plug-ins/1.10.11/i18n/Portuguese-Brasil.json"
        
      }
      
      DT::datatable(
        data = full_df,
        style = 'auto',
        class = 'cell-border stripe',
        caption = htmltools::tags$caption(
          style = 'caption-side: top;
                  text-align: center;
                  color:black;
                  font-size:200% ;
                  padding-top: 20px;
                  padding-bottom: 15px;',
          capt),
        rownames = FALSE,
        escape = FALSE,
        colnames = column_names,
        options = list(
          columnDefs = list(list(
            className = 'dt-center',
            targets = c(0)
          )),
          searchHighlight = TRUE,
          search = list(regex = TRUE),
          order = list(list(0, 'asc')),
          language = list(url = translate_to)
        )
      )
    
  }, error = function(e) {
    if (lang == "EN" || lang == "en") {
      err_msg <- paste0("Error: ",
                        "\n",
                        "Something went wrong. Please contact the maintainer.")
      
    } else {
      err_msg <- paste0("Erro: ",
                        "\n",
                        "Aconteceu um erro inesperado. Por favor entre em contacto com a equipa de desenvolvimento.")
      
    }
    stop(err_msg)
    
  })
    
}
```
  
```{r example-ya_get_dimension_description}
ya_get_dimension_description()
```
  
```{r tests-ya_get_dimension_description}
#'\dontrun{
#'test_that("ya_get_dimension_description works", {
#'  expect_true(inherits(ya_get_dimension_description, "function")) 
#'})
#'}
```
   

# ya_save_dimension_description()

This function allows saving the information about description of BPstat dimensions to an external file.
    
```{r function-ya_save_dimension_description}

#' Title ya_save_dimension_description()
#' 
#' Description: A function that saves de information available about the BPstat description of dimensions.
#' 
#' @param lang  A string that represents the languages supported by BPstat API. Currently only uses "PT" or "EN". Defaults to "EN"
#' @param extension A string that represents the available extensions to save files. Currently only uses "rds" or "csv". Defaults to "rds"
#'
#' @importFrom httr2 request
#' @importFrom httr2 req_user_agent
#' @importFrom httr2 req_perform
#' @importFrom httr2 resp_status
#' @importFrom httr2 resp_body_raw
#' @importFrom dplyr between
#' @importFrom dplyr tibble
#' @importFrom dplyr %>%
#' @importFrom jsonlite fromJSON
#' @importFrom tidyr drop_na
#' 
#' @return A file with the information about BPstat description of dimensions with the rds or csv extension.
#' 
#' @export
#' 
ya_save_dimension_description <- function(lang = "EN", extension = "rds"){
  
  check_language(lang)
  
  check_extension(extension)
  
  tmp_dset_df <- data.frame()
  
  temp_df <- data.frame()
  
  basepath_url <- "https://bpstat.bportugal.pt"
  
  url <- paste0(basepath_url,
                "/data/v1/domains/?lang=",
                toupper(lang))
  
  response <- httr2::request(url) %>% 
    httr2::req_user_agent("YABPstat package") %>% 
    httr2::req_perform()
  
  st_c <- httr2::resp_status(response)
  
  status_description <-
    check_status_code(st_c, lang)
  
  if (dplyr::between(st_c, 300, 550)) {
    stp_msg <- paste0("Estado :",
                      st_c,
                      " - ",
                      status_description,
                      ".")
    
    stop(stp_msg)
    
  } else {
    raw_response <- response %>% 
      httr2::resp_body_raw()
    
    temp_df <- jsonlite::fromJSON(rawToChar(raw_response))
    
    temp_df <- temp_df %>%
      dplyr::select(dimensions_href, num_series) %>%
      tidyr::drop_na()
    
    for (row in 1:nrow(temp_df)) {
      tmp_dset_df <- rbind(tmp_dset_df,
                           generate_dimensions(temp_df$dimensions_href[[row]]))
    }
    
    tmp_dset_df <- tmp_dset_df %>% dplyr::select(item_href)
    
    full_df <- dplyr::tibble()
    
    for (row in 1:nrow(tmp_dset_df)) {
      tryCatch({
        tmp_df <- NULL
        
        get_description <- httr2::request(tmp_dset_df[row, ]) %>% 
          httr2::req_user_agent("YABPstat package") %>% 
          httr2::req_perform()
        
        raw_get_description <- httr2::resp_body_raw(get_description)
        
        contents <-
          jsonlite::fromJSON(rawToChar(raw_get_description))
        
        tmp_lst <-
          do.call(rbind, contents$category$label)
        
        tmp_df <- as.data.frame(tmp_lst) %>%
          dplyr::rename(value = V1)
        
        tmp_df <-
          cbind(label = rownames(tmp_df), tmp_df)
        
        rownames(tmp_df) <- 1:nrow(tmp_df)
        
        tmp_df <-
          tmp_df %>% mutate(version = contents$version,
                            category_label = contents$label,
                            href = contents$href,
                            extension_id = contents$extension$id,
                            extension_description = contents$extension$description,
                            class = contents$class,
                            source = contents$source)
        
        full_df <- rbind(full_df, tmp_df)
        
      },
      error = function(e) {
        # There's no need for error message in simple export function
        # message("Erro: \n")
        # print(e)
        row = row + 1
      })
      
    }
    
    return(
      save_output(
        r_object = full_df,
        file_directory = "raw",
        file_name = "bpstat_domain_description",
        extension = extension
      )
    )
  }
  
    
}

```
  
```{r example-ya_save_dimension_description}
ya_save_dimension_description()
```
  
```{r tests-ya_save_dimension_description}
#'\dontrun{
#'test_that("ya_save_dimension_description works", {
#'  expect_true(inherits(ya_save_dimension_description, "function")) 
#'})
#'}
```


# ya_search()

This function allows to search BPstat through the API. The number of results are limited to 200.
    
```{r function-ya_search}

#' Title: ya_search()
#' 
#' Description: This is a function that allows to the user search directly de BPstat data through the API.

#' @param query A string that represents a query to be executed in BPstat
#' @param lang A string that represents the languages supported by BPstat API. Currently only uses "PT" or "EN". Defaults to "EN"
#' 
#' @importFrom utils URLencode
#' @importFrom httr2 request
#' @importFrom httr2 req_user_agent
#' @importFrom httr2 req_perform
#' @importFrom httr2 resp_status
#' @importFrom httr2 resp_body_json
#' @importFrom dplyr between
#' @importFrom dplyr tibble
#' @importFrom dplyr %>%
#' @importFrom dplyr select
#' @importFrom dplyr mutate
#' @importFrom dplyr relocate
#' @importFrom DT datatable
#' @importFrom htmltools tags
#' 
#' @return A data table with the query results from BPstat.
#' 
#' @export
#' 
ya_search <- function(query, lang = "EN"){
  
  check_language(lang)
  
  page_size <- 50
  
  basepath <-
    "https://bpstat.bportugal.pt/api/search/?search="
  
  q <- paste0(
    basepath,
    utils::URLencode(query),
    "&code=VET&language=",
    toupper(lang),
    "&page=1&page_size=",
    page_size
  )
  
  
  if (nchar(query) < 3) {
    
    if (lang == "EN" || lang == "en") {
      err_msg <- paste0(
        "Not enough letters to make a query.",
        "\n",
        "To obtain any results, please use more than 3 characters in the query."
      )
      
    } else {
      err_msg <-
        paste0(
          "N\u00famero de caracteres insuficiente para realizar a pesquisa.",
          "\n",
          "Para obten\u00e7\u00e3o de resultados, por favor utilize termos de pesquisa com, pelo menos, 3 caracteres."
        )
      
    }
    stop(err_msg)
    
  } else if (nchar(query) > 200) {
    stop("The query is limited to 200 characters. Please choose the words wisely.")
    
  }
  
  response <- httr2::request(q) %>%
    httr2::req_user_agent("YABPstat package") %>%
    httr2::req_perform()
  
  st_c <- httr2::resp_status(response)
  
  status_description <-
    check_status_code(st_c, lang)
  
  if (dplyr::between(st_c, 300, 550)) {
    stp_msg <- paste0("Estado :",
                      st_c,
                      " - ",
                      status_description,
                      ".")
    
    stop(stp_msg)
    
  }
  
  raw_response <-  response %>% 
    httr2::resp_body_json()

  if (raw_response$count == 0) {
    message("There's no results to show.")
    
  } else {
    if ((raw_response$count - 1) < page_size) {
      num_pages <- 1
      
    } else if ((raw_response$count - 1) > page_size) {
      if (((raw_response$count - 1) %% page_size) == 0) {
        num_pages <- as.integer((raw_response$count - 1) / page_size)
        
      } else {
        num_pages <- as.integer(((raw_response$count - 1) / page_size) + 1)
        
      }
      
    }
    
    tryCatch({
      results_df <- dplyr::tibble()
      
      for (pag in 1:num_pages) {
        
        results <- NULL
        
        q <- paste0(basepath,
                    utils::URLencode(query),
                    "&code=VET&language=",
                    toupper(lang),
                    "&page=",
                    pag,
                    "&page_size=",
                    page_size)

        results <- httr2::request(q) %>% 
          httr2::req_user_agent("YABPstat package") %>% 
          httr2::req_perform() %>% 
          httr2::resp_body_json()

        results_df <-
          rbind(results_df, as.data.frame(do.call(rbind, results$data)))
        
      }
      
      if (lang == "EN" || lang == "en") {
        column_names <- c("Link", "Title", "Description", "Publication")
        
        capt <- "YABPstat: Search results"
        
        translate_to <-
          '//cdn.datatables.net/plug-ins/1.10.11/i18n/English.json'
        
      } else {
        column_names <-
          c(
            "Liga\u00e7\u00e3o",
            "T\u00edtulo",
            "Descri\u00e7\u00e3o",
            "Publica\u00e7\u00e3o"
          )
        
        capt <- "YABPstat: Resultados da pesquisa"
        
        translate_to <-
          '//cdn.datatables.net/plug-ins/1.10.11/i18n/Portuguese-Brasil.json'
        
      }
      
      results_df <- results_df %>%
        dplyr::select(id, title, description, pub_date) %>%
        dplyr::mutate(
          link = paste0(
            "<a href=https://bpstat.bportugal.pt/serie/",
            id,
            " target=\"_blank\">",
            id,
            "</a>"
          )
        ) %>%
        dplyr::relocate(link, .before = title) %>%
        dplyr::select(-c(id))
      
      
      DT::datatable(
        data = results_df,
        style = 'auto',
        class = 'cell-border stripe',
        caption = htmltools::tags$caption(
          style = 'caption-side: top;
                        text-align: center;
                        color:black;  font-size:200% ;
                        padding-top: 20px;
                        padding-bottom: 15px;',
          capt
        ),
        rownames = FALSE,
        escape = FALSE,
        colnames = column_names,
        options = list(
          columnDefs = list(list(
            className = 'dt-center', targets = c(0)
          )),
          searchHighlight = TRUE,
          search = list(regex = TRUE),
          language = list(url = translate_to)
        )
      )
      
    }, error = function(e) {
      if (lang == "EN" || lang == "en") {
        err_msg <- paste0("Error: ",
                          "\n",
                          "Something went wrong. Please contact the maintainer.")
        
      } else {
        err_msg <- paste0(
          "Erro: ",
          "\n",
          "Aconteceu um erro inesperado. Por favor entre em contacto com a equipa de desenvolvimento."
        )
        
      }
      stop(err_msg)
      
    })
  }
}

```
  
```{r example-ya_search}
ya_search(query="ihpc")
```
  
```{r tests-ya_search}
#'\dontrun{
#'test_that("ya_search works", {
#'  expect_true(inherits(ya_search, "function")) 
#'})
#'}
```
  


# ya_my_favourites()

This function allows user management of favourite series ID from BPstat.
    
```{r function-ya_my_favourites}
#'
#' Title: ya_my_favourites()
#' 
#' Description: this function allows user to add, delete and view favourite series from BPStat
#' 
#' @param series_id A serie ID from BPstat. Defaults to 0 (zero)
#' @param operation A string with the length of 1 (one), representing the following operations:
#'                      A - add
#'                      D - delete
#'                      V - view
#' @param lang  A string that represents the languages supported by BPstat API. Currently only uses "PT" or "EN". Defaults to "EN"
#' 
#' @importFrom httr2 request
#' @importFrom httr2 req_user_agent
#' @importFrom httr2 req_perform
#' @importFrom httr2 resp_body_json
#' @importFrom httr2 resp_status
#' @importFrom dplyr tibble
#' @importFrom dplyr between
#' @importFrom dplyr %>%
#' @importFrom DT datatable
#' 
#' @return A file named ya_favourites with user favourite series
#' 
#' @export
#' 
ya_my_favourites <- function(series_id = 0, operation = "V", lang = "EN"){
  
  check_language(lang)
  
  fich <- system.file("ya_favourites.rds",package = "yabpstat", mustWork = TRUE)
  
  favourites <- readRDS(file = fich)
  
  
  if (!(operation %in% c("A", "a", "D", "d", "V", "v"))) {
    stop(
      "Wrong type of operation. \nPlease choose between \"A\" - add, \"D\" - delete and \"V\" - view."
    )
  }
  
  if ((operation == "A" |
       operation == "a") & !(series_id == 0)) {
    add_favourite(id = series_id, dataset = favourites)
    
  } else if ((operation == "D" |
             operation == "d") & !(series_id == 0)) {
    delete_favourite(id = series_id, dataset = favourites)
    
  } else if ((operation == "V" |
              operation == "v") & (series_id == 0)) {
    basepath <-
      "https://bpstat.bportugal.pt/data/v1/series/?lang="
    
    vec_favourites <-
      paste(apply(favourites, 1, function(x)
        paste(x, collapse = ",")), collapse = ",")
    
    url_favourites <- paste0(basepath,
                             toupper(lang),
                             "&series_ids=",
                             vec_favourites)
    
    if (nchar(url_favourites) > 2048) {
      stop("The URL is limited to 2048 characters. Too many favourites stored.")
    }
    
    tryCatch({
      df_favourites <- dplyr::tibble()
      
      response <- httr2::request(url_favourites) %>%
        httr2::req_user_agent("YABPstat package") %>%
        httr2::req_perform()
      
      content <- response %>%
        httr2::resp_body_json()
      
      st_c <-
        httr2::resp_status(response)
      
      status_description <-
        check_status_code(st_c, lang)
      
      if (dplyr::between(st_c, 300, 550)) {
        stp_msg <- paste0("Estado :",
                          st_c,
                          " - ",
                          status_description,
                          ".")
        
        stop(stp_msg)
        
        
      } else {
        for (number in 1:nrow(favourites)) {
          id <- content[[number]][["id"]]
          
          descricao <-
            content[[number]][["description"]]
          
          etiqueta <-
            content[[number]][["label"]]
          
          abreviatura <-
            content[[number]][["short_label"]]
          
          atualizacao <-
            content[[number]][["obs_updated_at"]]
          
          new_row <- dplyr::tibble(id,
                                   descricao,
                                   etiqueta,
                                   abreviatura,
                                   atualizacao)
          
          df_favourites <-
            rbind(df_favourites, new_row)
          
        }
        
        if (lang == "EN" | lang == "en") {
          column_names <-
            c("ID",
              "Description",
              "Label",
              "Short label",
              "Updated at")
          
          capt <- "YABPstat: My favourite series"
          
          translate_to <-
            "//cdn.datatables.net/plug-ins/1.10.11/i18n/English.json"
          
        } else {
          column_names <-
            c(
              "ID",
              "Descri\u00e7\u00e3o",
              "Etiqueta",
              "Abreviatura",
              "Atualiza\u00e7\u00e3o em"
            )
          
          capt <-
            "YABPstat: As minhas s\u00e9ries favoritas"
          
          translate_to <-
            "//cdn.datatables.net/plug-ins/1.10.11/i18n/Portuguese-Brasil.json"
          
        }
        
        DT::datatable(
          data = df_favourites,
          style = 'auto',
          class = 'cell-border stripe',
          caption = htmltools::tags$caption(
            style = 'caption-side: top;
                    text-align: center;
                    color:black;
                    font-size:200% ;
                    padding-top: 20px;
                    padding-bottom: 15px;',
            capt
          ),
          rownames = FALSE,
          escape = FALSE,
          colnames = column_names,
          options = list(
            columnDefs = list(list(
              className = 'dt-center',
              targets = c(0)
            )),
            searchHighlight = TRUE,
            search = list(regex = TRUE),
            order = list(list(0, 'asc')),
            language = list(url = translate_to)
          )
        )
      }
      
    }, error = function(e) {
      if (lang == "EN" || lang == "en") {
      err_msg <- paste0("Error: ",
                        "\n",
                        "Something went wrong. Please contact the maintainer.")
      
    } else {
      err_msg <- paste0("Erro: ",
                        "\n",
                        "Aconteceu um erro inesperado. Por favor entre em contacto com a equipa de desenvolvimento.")
      
    }
    stop(err_msg)
      
    })
    
  } else {
    stop("Please check your arguments. There's something wrong.")
  }  
     
}
```
  
```{r example-ya_my_favourites}
ya_my_favourites()
```
  
```{r tests-ya_my_favourites}
#'\dontrun{
#' test_that("ya_my_favourites works", {
#'   expect_true(inherits(ya_my_favourites, "function")) 
#' })
#' }
```
  
# ya_info_serie()

This function allows to user to plot, see in a table or reuse in other context, data from a determined BPstat serie ID.
    
```{r function-ya_info_serie}
#'
#' Title: ya_info_serie()
#' 
#' Description: A function allows to user to plot, see in a table or reuse in other context, data from a determined BPstat serie ID.
#' 
#' @param series_id A serie ID from BPstat. Defaults to 0 (zero)
#' @param operation A string with the length of 1 (one), representing the following operations:
#'                      P - plot
#'                      T - table
#'                      Df - dataframe
#' @param lang  A string that represents the languages supported by BPstat API. Currently only uses "PT" or "EN". Defaults to "EN"
#' 
#' @importFrom httr2 request
#' @importFrom httr2 req_user_agent
#' @importFrom httr2 req_perform
#' @importFrom httr2 resp_status
#' @importFrom dplyr between
#' @importFrom dplyr %>%
#' @importFrom dplyr tibble
#' @importFrom dplyr mutate
#' @importFrom dplyr across
#' @importFrom dplyr select
#' @importFrom tidyr unnest_longer
#' @importFrom tidyr unnest_wider
#' @importFrom jsonlite read_json
#' 
#' @return From the user choice can be a plot, a table or a tibble for further analysis
#' 
#' @export
#' 
ya_info_serie <- function(series_id = 0, operation = "P", lang = "EN"){
  
  check_language(lang)
  
  if (!(operation %in% c("P", "p", "T", "t", "Df", "df"))) {
    stop(
      "Wrong type of operation. \nPlease choose between \"P\" - plot, \"T\" - table and \"Df\" - dataframe."
    )
  }
  
  if ((operation == "P" |
       operation == "p") & !(series_id == 0)) {
    plot_serie(id = series_id, lng = lang)
    
  } else if ((operation == "T" |
             operation == "t") & !(series_id == 0)) {
    data_serie(id = series_id, lng = lang)
    
  } else if ((operation == "Df" |
             operation == "df") & !(series_id == 0)) {
    df_data <- dplyr::tibble()
    
    basepath <- "https://bpstat.bportugal.pt"
    
    url_sv <- paste0(basepath,
                     "/api/observations/?series_ids=",
                     series_id)
    
    response <- httr2::request(url_sv) %>% 
      httr2::req_user_agent("YABPstat package") %>% 
      httr2::req_perform()
    
    st_c <- httr2::resp_status(response)
    
    status_description <-
      check_status_code(st_c, lang)
    
    if (dplyr::between(st_c, 300, 550)) {
      stp_msg <- paste0("Estado :",
                        st_c,
                        " - ",
                        status_description,
                        ".")
      
      stop(stp_msg)
    }
    
    url_sv_json <- jsonlite::read_json(url_sv)
    
    df_data <- url_sv_json %>%
      dplyr::tibble() %>%
      tidyr::unnest_longer(1) %>%
      tidyr::unnest_wider(1) %>%
      dplyr::mutate(dplyr::across(reference_date, as.Date),
                    dplyr::across(pub_date, as.Date)) %>%
      dplyr::select(-c(series_id, privacy_code, is_highlighted, description))
    
    return(df_data)
    
    message(
      "The dataframe contains the following variables:\n
                id,\n
                version_id,\n
                value,\n
                reference_date,\n
                pub_date."
    )
    
  } else {
    stop("Please check your arguments. There's something wrong.")
  }
 
}
```
  
```{r example-ya_info_serie}
ya_info_serie(series_id = 12528985)
```
  
```{r tests-ya_info_serie}
#'\dontrun{
# test_that("ya_info_serie works", {
#   expect_true(inherits(ya_info_serie, "function")) 
# })
#'}
```
